Smart Drill-Down: Interactive Summarization of Relational Tables

### 2014-11-15 TableSummarization/Paper/algorithms.tex
small changes
small suggestions

\section{Algorithms}
\label{sec:algorithms}
When the user drills down on a rule $r^{\prime}$, we want to find the highest scoring list of rules to expand rule $r^{\prime}$ into. If the user had clicked on a $\star$ in a column $c$, then we have the additional restriction that all resulting rules must have a non-$\star$ value in column $c$. We can reduce Problem~\ref{prob:optimal-subrule-list} to the following simpler problem by removing the user-interaction based constraints:

@@

$W$ is required to be non-negative and monotonic. $k$ will usually be small (though the correctness of our solution does not depend on this), since the $k$ rules generated should constitute an easily visualizable summary of the table.

Problem~\ref{prob:optimal-subrule-list} with parameters $(T, W, k)$ can be reduced to Problem~\ref{prob:optimal-rule-list} as follows:
\squishlist
\item $[$Rule Drill-Down$]$ If the user clicked on rule $r$ in Problem~\ref{prob:optimal-subrule-list}, then we make on pass through the table $T$ to filter for tuples covered by rule $r$, and store them in a temporary table $T_r$. Then we solve Problem~\ref{prob:optimal-rule-list} for parameters $(T_r, W, k)$.
\item $[$Star Drill-Down$]$ If the user clicked on a $\star$ in column $c$ of rule $r$, then we first filter table $T$ to get $T_r$ consisting of tuples from $T$ that are covered by $r$. In addition, we change the weight function $W$ from Problem~\ref{prob:optimal-subrule-list} to a weight function $W^{\prime}$ such that : For any rule $r^{\prime}$, $W^{\prime}(r^{\prime}) = 0$ if $r^{\prime}$ has a $\star$ in column $c$, and $W^{\prime}(r^{\prime}) = W(r^{\prime})$ otherwise. Then we solve Problem~\ref{prob:optimal-rule-list} for parameters $(T_r, W^{\prime}, k)$.
\squishend

We will describe a greedy algorithm for finding the approximately highest scoring rule-list. First, we show that the rules in the optimal list must effectively be ordered in decreasing order by weight.

@@

Thus it is sufficient to restrict our attention to rule-lists that have rules sorted in decreasing order by weight. Or equivalently, given any set $S$ of rules, we can define the Score$(S)$ to be the score of the list obtained by sorting elements of $S$ in decreasing weight order. This gives us 
\begin{problem}\label{prob:optimal-rule-set}
Given a table $T$, a weight function $W$, and a number $k$, to find the set $R$ of $k$ rules such that if $R^{\prime}$ is the rule-list obtained by ordering rules in $R$ in decreasing weight order, then the following quantity is maximised:
$$\text{Score}(R) = \text{Score}(R^{\prime}) = \sum_{r \in R^{\prime}}W(r)MCount(r,R)$$
\end{problem}

The reduction from Problem~\ref{prob:optimal-rule-list} to Problem~\ref{prob:optimal-rule-set} is clear. We now show an approximation algorithm for Problem~\ref{prob:optimal-rule-set}.

\subsection{Greedy approximation algorithm for Problem~\ref{prob:optimal-rule-set}}
We will now show that the Score function over sets of rules has a property called {\em submodularity}, which gives us a greedy approximation algorithm for optimizing it. 
\begin{definition}
A function $f: 2^S \rightarrow \mathbb{R}$ for any set $S$ is said to be submodular if and only if, for every $s \in S$, and $A \subset B \subset S$ with $s \notin A$:
$$f(A \cup \left\lbrace s \right\rbrace) - f(A) \geq f(B \cup \left\lbrace s \right\rbrace) - f(B)$$
\end{definition}
Intuitively, this means that the marginal value of adding an element to a set $S$ cannot increase if we add it to a superset of $S$ instead. For monotonic non-negative submodular functions, the problem of finding the set of a given size with maximum value for the function can be found approximately in a greedy way.

@@

\begin{framed}
\begin{enumerate}
\item Set $S = \phi$
\item For $i$ from $1$ to $k$
\begin{enumerate}
\item Find the rule $r$ for which Score($S \cup \left\lbrace r \right\rbrace$) is the highest.
\item $S = S \cup \left\lbrace r \right\rbrace$
\end{enumerate}
\end{enumerate}
\end{framed}

@@

\subsection{Sampling for big tables}
Our greedy algorithm needs to make multiple passes over the entire table in order to find counts of rules. These passes can be very expensive if the table is large, especially if it does not fit in main memory. If we want exact counts for rules, we have no choice but to read the entire table.

@@

Thus formally our problem is :
Choose an integer $n_r \geq 0$ for each $r \in U$ so as to $\textrm{maximize}$ :
$$\sum_{r^{\prime} \in L} p_{r^{\prime}}I_{\text{ess}(r^{\prime}) \geq \text{minSS}}$$
where the $I$'s are indicator variables, subject to :
$$\sum_{r \in U} n_r < \text{capacity}$$
This problem is non-linear and non-convex because of the indicator variables. If the tree $U$ is not too big, then it might be feasible to use an exponential algorithm to solve the problem.

>>>>

\section{Smart Drill-Down Algorithms}
\label{sec:algorithms}
We now describe online algorithms for implementing
the smart drill-down operator.

\subsection{Problem Reduction and Important Property} \label{sec:reduction}
When the user drills down on a rule $r^{\prime}$, we want to find the highest scoring list of rules to expand rule $r^{\prime}$ into. If the user had clicked on a $\star$ in a column $c$, then we have the additional restriction that all resulting rules must have a non-$\star$ value in column $c$. We can reduce Problem~\ref{prob:optimal-subrule-list} to the following simpler problem by removing the user-interaction based constraints:

@@

\agp{not essential to mention here.}
\sout{$W$ is required to be non-negative and monotonic. $k$ will usually be small (though the correctness of our solution does not depend on this), since the $k$ rules generated should constitute an easily visualizable summary of the table.}

\noindent Problem~\ref{prob:optimal-subrule-list} with parameters $(T, W, k)$ can be reduced to Problem~\ref{prob:optimal-rule-list} as follows:
\squishlist
\item $[$Rule Drill-Down$]$ If the user clicked on rule $r$ in Problem~\ref{prob:optimal-subrule-list}, then we can conceptually make one pass through the table $T$ to filter for tuples covered by rule $r$, and store them in a temporary table $T_r$. Then we solve Problem~\ref{prob:optimal-rule-list} for parameters $(T_r, W, k)$.
\item $[$Star Drill-Down$]$ If the user clicked on a $\star$ in column $c$ of rule $r$, then we first filter table $T$ to get a smaller table $T_r$ consisting of tuples from $T$ that are covered by $r$. In addition, we change the weight function $W$ from Problem~\ref{prob:optimal-subrule-list} to a weight function $W^{\prime}$ such that : For any rule $r^{\prime}$, $W^{\prime}(r^{\prime}) = 0$ if $r^{\prime}$ has a $\star$ in column $c$, and $W^{\prime}(r^{\prime}) = W(r^{\prime})$ otherwise. Then we solve Problem~\ref{prob:optimal-rule-list} for parameters $(T_r, W^{\prime}, k)$.
\squishend

\agp{not essential to mention here}\sout{We will describe a greedy algorithm for finding the approximately highest scoring rule-list.}

First, we show that the rules in the optimal list must effectively be ordered in decreasing order by weight.
\agp{mention that this is independent of MCount. Also give intuition--this is because
we can transfer tuples from one rule to a better rule adn only increase score.}

@@

\noindent Thus it is sufficient to restrict our attention to rule-lists that have rules sorted in decreasing order by weight. Or equivalently, given any set $S$ of rules, we can define the Score$(S)$ to be the score of the list obtained by sorting elements of $S$ in decreasing weight order. This gives us 
\begin{problem}\label{prob:optimal-rule-set}
Given a table $T$, a weight function $W$, and a number $k$, to find the set $R$ of $k$ rules such that if $R^{\prime}$ is the rule-list obtained by ordering rules in $R$ in decreasing weight order, then the following quantity is maximised:
$$\text{Score}(R) = \text{Score}(R^{\prime}) = \sum_{r \in R^{\prime}}W(r)MCount(r,R)$$
\end{problem}

\agp{Confusing since you're conflating lists and sets. Explicitly define the score of a set of rules
is the score of the best rule list (and in the equation above, have max over all R' where R' is an ordered
version of S)}

\noindent The reduction from Problem~\ref{prob:optimal-rule-list} to Problem~\ref{prob:optimal-rule-set} is clear. We now show an approximation algorithm for Problem~\ref{prob:optimal-rule-set}.

\subsection{Algorithm Overview}\label{sec:alg-overview}
\agp{Give a high-level perspective of the algorithm; 
Basics: greedy approximation + a-priori; 
Advanced: Sampling for larger datasets: comprising two parts
how to best use samples, and how to select samples}

\subsection{Greedy Approximation Algorithm}\label{sec:greedy-approx}
\agp{can we show hardness in data or schema complexity?}
We will now show that the Score function over sets of rules has a property called {\em submodularity}, which gives us a greedy approximation algorithm for optimizing it. 
\begin{definition}
A function $f: 2^S \rightarrow \mathbb{R}$ for any set $S$ is said to be submodular if and only if, for every $s \in S$, and $A \subset B \subset S$ with $s \notin A$:
$$f(A \cup \left\lbrace s \right\rbrace) - f(A) \geq f(B \cup \left\lbrace s \right\rbrace) - f(B)$$
\end{definition}
Intuitively, this means that the marginal value of adding an element to a set $S$ cannot increase if we add it to a superset of $S$ instead. For monotonic non-negative submodular functions, the problem of finding the set of a given size with maximum value for the function can be found approximately in a greedy way.

@@

\begin{framed}
\vspace{-15pt}
\begin{enumerate}
\item Set $S = \phi$
\item For $i$ from $1$ to $k$
\begin{enumerate}
\item Find the rule $r$ for which Score($S \cup \left\lbrace r \right\rbrace$) is the highest.
\item $S = S \cup \left\lbrace r \right\rbrace$
\end{enumerate}
\end{enumerate}
\vspace{-15pt}
\end{framed}

@@

\subsection{Sampling for big tables}

\agp{Here also, there is a need for some organization. There are clearly
some good ideas here, but you need to give a high-level picture first before
diving in.}
Our greedy algorithm needs to make multiple passes over the entire table in order to find counts of rules. These passes can be very expensive if the table is large, especially if it does not fit in main memory. If we want exact counts for rules, we have no choice but to read the entire table.

@@

\agp{not clear what problem you're trying to solve here. consider raising it up as a subsection
and giving it a name. }
Thus formally our problem is :
Choose an integer $n_r \geq 0$ for each $r \in U$ so as to $\textrm{maximize}$ :
$$\sum_{r^{\prime} \in L} p_{r^{\prime}}I_{\text{ess}(r^{\prime}) \geq \text{minSS}}$$
where the $I$'s are indicator variables, subject to :
$$\sum_{r \in U} n_r < \text{capacity}$$
This problem is non-linear and non-convex because of the indicator variables. If the tree $U$ is not too big, then it might be feasible to use an exponential algorithm to solve the problem.

### 2014-11-15 TableSummarization/Paper/exp.tex
small suggestions

>>>>

\agp{I propose using two sections: one is Qualitative Study, which will contain 4.2, 4.3, and 
Quantitiative Study, whcih will contain the rest of the sections.
For the quantitative study, mention that the goal of the experimental evaluation is to study
the impact of the two parameters on time and accuracy before you get into details.
Maybe also good to fix mw, and show the performance with or without sampling,
and with or without a-priori (one rule per phase, for instance).
}
